Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce

### 2019-08-23 sample-sigchi.tex
update

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

>>>>

\section{Introduction}

An important goal in distributed-systems design is to construct a system in such a way it can provide its services even in the presence of faults. In other words, whenever a failure
occurs, the system should continue to operate in an acceptable way; that is a distributed system is expected to be \textit{fault tolerant}. As known, many fault types exists in literature, the most serious of which are \textit{arbitrary failures}, also known as \textit{Byzantine failures}; whenever a that type of fault occurs, a server may produce arbitrary responses at arbitrary times which cannot be detected as being incorrect.

In this paper we present an Arbitrary Fault-Tolerant (AFT) MapReduce runtime system.

The key technique used to manage faults is, as , to use redundancy.The key approach to tolerating a faulty process is to organize several identical processes into a group.

 Our BFT
MapReduce follows the approach of executing each task more
than once, similarly to the works mentioned above. The chal-

Process groups are part of the solution for building fault-tolerant systems.
In particular, having a group of identical processes allows us to mask one
or more faulty processes in that group. In other words, we can replicate
processes and organize them into a group to replace a single (vulnerable)
process with a (fault tolerant) group.

An important issue with using process groups to tolerate faults is how
much replication is needed. To simplify our discussion, let us consider
only replicated-write systems. A system is said to be k-fault tolerant if it
can survive faults in k components and still meet its specifications. If the
components, say processes, fail silently, then having k + 1 of them is enough
to provide k-fault tolerance. If k of them simply stop, then the answer from
the other one can be used.

On the other hand, if processes exhibit arbitrary failures, continuing to
run when faulty and sending out erroneous or random replies, a minimum
of 2k + 1 processes are needed to achieve k-fault tolerance. In the worst case,
the k failing processes could accidentally (or even intentionally) generate the
same reply. However, the remaining k + 1 will also produce the same answer,
so the client or voter can just believe the majority.

\section{Template Overview}

\subsection{System Architecture}

Our system is composed by a set of distributed processes:

\begin{description}
\item[Client Process] the clients that request the execution of jobs composed by map and reduce tasks

\item[Leader Primary Process] It manages the execution of word-count jobs received from clients coordinating Worker Nodes

\item[Backup Primary Process] It manages the execution of word-count jobs received from clients coordinating Worker Nodes

\item[Worker Process] A Worker Process executes map and reduce task

\item[Worker Group] All system's nodes in which worker process are running are logically split into several \textit{Groups}, that is sets of equal worker processes, each of which execute the same commands using same input data in the same order. In a group all worker processes run independently on different host and they do not interact with each other in any way. Current Leader Primary Process can interact with groups members using a push-based approach in order to schedule map or reduce tasks. Although, for performance reasons, not always happen, when a task is sent to the group itself, all members of the group receive it.

The key property that all groups have is that when a
message is sent to the group itself, all members of the group receive it.

 primary coordinates all write
operations

 In other words, we can replicate processes and organize them into a group to replace a single (vulnerable) process with a (fault tolerant) group.

 When a task is  for work is generated, either
by an external client or by one of the workers, it is sent to the coordinator.

as  a set of Task- Trackers that execute tasks
\end{description}

We assume that clients are always correct, because if they are not there is no point in worrying about the correctness of the job’s output.

The host where current master process is running may fail, for example by crashing or by losing network connectivity. Therefore, to ensure system availability in such a way that it can keep on providing its services, multiple master process copies of run on different host, and that a backup copy is promoted to become the new leader when the previous leader fails.

In order to decide when the current leader master process has failed and to elect a new leader, we have used a coordination service like Apache ZooKeeper.

The Mesos master stores information about the active tasks and registered frameworks in memory: it does not persist it to disk or attempt to ensure that this information is preserved after a master failover. This helps the Mesos master scale to large clusters with many tasks and frameworks. A downside of this design is that after a failure, more work is required to recover the lost in-memory master state.

 Mesos consists of a master daemon that manages agent daemons running on each cluster node, and Mesos frameworks that run tasks on these agents.

The Mesos master stores information about the active tasks and registered frameworks in memory: it does not persist it to disk or attempt to ensure that this information is preserved after a master failover. This helps the Mesos master scale to large clusters with many tasks and frameworks. A downside of this design is that after a failure, more work is required to recover the lost in-memory master state.

System model. The system is composed by a set of dis-
tributed processes: the clients that request the execution of
jobs composed by map and reduce tasks, the JobTracker that
manages the execution of a job as explained, a set of Task-
Trackers that execute tasks, the NameNode that manages ac-
cess to data stored in HDFS, and a set of DataNodes where
HDFS stores file blocks. We say that a process is correct if
it follows the algorithm, otherwise we say it is faulty. We
also use these two words to denominate a task (map or re-
duce) that, respectively, returns the result that corresponds to
an execution in a correct TaskTracker (correct) or not (faulty).
Processes run in servers in a datacenter.
